# Developing Data Products Week 3 R Markdown Presentation & Plotly

# BHARATH KUMAR R
# 10-03-2020


1. I created a two graghs using plotly library.

2. In first graph its tells about plotting markers and lines in graph you can fing three things called        trace 0, trace 1 and trace 2.

# Plotting Markers and Lines

```{r}
library(plotly)

trace_0 <- rnorm(100, mean = 5) 
trace_1 <- rnorm(100, mean = 0)
trace_2 <- rnorm(100, mean = -4)
x <- c(1:100)

data <- data.frame(x, trace_0, trace_1, trace_2)

fig <- plot_ly(data, x = ~x)
fig <- fig %>% add_trace(y = ~trace_0, name = 'trace 0',mode = 'lines')
fig <- fig %>% add_trace(y = ~trace_1, name = 'trace 1', mode = 'lines+markers')
fig <- fig %>% add_trace(y = ~trace_2, name = 'trace 2', mode = 'markers')

fig
```





# Adding Color and Size Mapping

1. This is my second graph by using library plotly.

2. In this graph i used color and size to make graph more attractive on x-axis carat and on y-axis price.

```{r}

library(plotly)

d <- diamonds[sample(nrow(diamonds), 1000), ]

fig <- plot_ly(
  d, x = ~carat, y = ~price,
  color = ~carat, size = ~carat
)

fig
```